\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistatic control of gene expression in Humans\\[0.3cm] \huge *** Report V1 *** \\ \horrule{2pt} \\[0.5cm]

### 2013-04-24 docs/manuscript/report_v1.tex
minor chnages to the figure legends and text

\begin{table}[ht]
	\centering
	\begin{tabular}{rlr}
		\hline
		& Interaction type & Freq \\ 
		\hline
		1 & cis-cis &  32 \\ 
		2 & cis-trans & 388 \\ 
		3 & trans-trans &  12 \\ 
		\hline
	\end{tabular}
	\label{tab:type}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{rlr}
		\hline
		& Main epistatic effect & Freq \\ 
		\hline
		1 & A x A &  99 \\ 
		2 & A x D &  93 \\ 
		3 & D x A & 117 \\ 
		4 & D x D & 123 \\ 
		\hline
	\end{tabular}
	\label{tab:vc}
\end{table}

\begin{figure}[p]
	\centering
	\includegraphics[width=15cm]{images/3dplots}
	\caption{Genotype-phenotype maps for the nine most significant interactions.}
	\label{fig:3dplots}
\end{figure}

>>>>

\begin{table}[ht]
	\centering
	\begin{tabular}{rlr}
		\hline
		& Interaction type & Freq \\ 
		\hline
		1 & $cis-cis$ &  32 \\ 
		2 & $cis-trans$ & 388 \\ 
		3 & $trans-trans$ &  12 \\ 
		\hline
	\end{tabular}
	\caption{Epistasis pair positions. Here $cis$ SNPs are on the same chromosome as the probe. $Trans$ SNPs are on a different chromosome}
	\label{tab:type}
\end{table}

\begin{table}[ht]
	\centering
	\begin{tabular}{rlr}
		\hline
		& Main epistatic effect & Freq \\ 
		\hline
		1 & A x A &  99 \\ 
		2 & A x D &  93 \\ 
		3 & D x A & 117 \\ 
		4 & D x D & 123 \\ 
		\hline
	\end{tabular}
	\caption{The largest epistatic variance component was recorded for each pair. This table summerises how often each type of epistatic variance occurs}
	\label{tab:vc}
\end{table}

\begin{figure}[p]
	\centering
	\includegraphics[width=15cm]{images/3dplots}
	\caption{Genotype-phenotype maps for the nine most significant interactions. p1 and p2 are MAF for SNP 1 and SNP 2 respectively}
	\label{fig:3dplots}
\end{figure}
